Interactively Visualizing Multivariate Market Segmentation Using the R Package Lionfish

### 2024-10-02 manuscript.tex
response to Uschis comments. minor adjustments to 2.1 and the heatmap mini example

At the top of the sidebar, users can select and deselect features using checkboxes (Figure \ref{fig:GUI_overview}C), controlling which features are displayed in the plots. Below this, each subset has its own checkbox to designate the active subset (Figure \ref{fig:GUI_overview}D). When data points are manually selected in the plots, they will be assigned to the active subset and colored accordingly. For scatterplots, data points can be selected by encircling them directly on the plot while holding down the left mouse button. For barplots, clicking on a specific bar selects the data represented by that bar. The colored boxes next to the subset names indicate the assigned colors for the data points. Clicking on these boxes adjusts the transparency of the points, which is helpful for highlighting and comparing subsets. Subsets can also be renamed using the provided text boxes. The \texttt{Reset original selection} button allows users to revert the subset selections to their initial state.

@@

The \texttt{Save projections and subsets} button can be used to save the current state of the analysis. These states can be recovered by using pressing the \texttt{Load projections and subsets} button. Additionally, users can initiate new tours directly from the sidebar. The options for new tour paths are: a local tour around the currently shown projection, a guided tour that searches for projections with maximum separation between groups \textcolor{red}{XXX is this true? other options?}

@@

\textcolor{red}{Maybe here you can say something about adding new display types, what would be needed for implementing them}

@@

The second, $f^c$ is normalized relative to the size of each cluster and can be considered the distribution of features in each cluster. It is useful for comparing the composition of each cluster relative to the features. For example, for $p=4$, if $f^c_{1j} = (0.4, 0.4, 0.1, 0.1)$ it suggests that high values (1's) of features 1 and 2 distinguish cluster 1. In the context of the later examples, this would mean cluster 1 contains tourists that list engaging in activities 1 and 2 but not 3 and 4. This normalisation produces what is called the {\bf intra-cluster fraction}. \textcolor{red}{It corresponds to the cluster means. XXX why not larger values in the example, the maximum would be 1 so 0.4 still seems very moderate.}

The last, $f^f$ is normalized relative to each feature, which can be considered to be the distribution of clusters on each feature. It is useful to examine how features are related to a cluster. Considering the last metric, for example, if $f^f_{i1} = (0.5, 0.4, 0, 0.1, 0)$ ($k=5$) would indicate that high values on feature 1 primarily are in clusters 1, 2. In the context of the later examples, this would mean activity 1 is commonly listed only in clusters 1 and 2. This normalisation produces what is called the {\bf intra-feature fraction}. \textcolor{red}{Note that this must be interpreted with care in case of inbalanced cluster sizes.}

>>>>

At the top of the sidebar, users can select and deselect features using checkboxes (Figure \ref{fig:GUI_overview}C), controlling which features are displayed in the plots. Below this, each subset has its own checkbox to designate the active subset (Figure \ref{fig:GUI_overview}D). When data points are manually selected in the plots, they will be assigned to the active subset and colored accordingly. For scatterplots, data points can be selected by encircling them directly on the plot while holding down the left mouse button. For barplots, clicking on a specific bar selects the data represented by that bar. The colored boxes next to the subset names indicate the assigned colors for the data points. Clicking on these boxes adjusts the transparency of the points, which is helpful for highlighting and comparing subsets. Subsets can also be renamed using the provided text boxes. The \texttt{Reset original selection} button allows users to revert the subset selections to their initial state. All plots displayed in the GUI are linked, meaning that changes in one plot will affect the other plots. For instance, if observations are moved from one subset into another subset in one plot then the reassigment will also occur in the other plots.

@@

The \texttt{Save projections and subsets} button can be used to save the current state of the analysis. These states can be recovered by using pressing the \texttt{Load projections and subsets} button. Additionally, users can initiate new tours directly from the sidebar. The options for new tour paths are: a local tour around the currently shown projection and guided tours that search for projections based on the holes- or the linear discriminant analysis (LDA) index. The holes index is sensitive to projections with few points in the center of the projections and the LDA index aims to maximize the distance between the centers of the selectet subsets. \textcolor{red}{XXX is this true? other options?} Additionally, all tour displays allow users to perform a manual tour; by right-clicking and dragging the arrowheads of projection axes, the projection is recalculated accordingly. This allows for manual exploration of the data.

@@

\textcolor{red}{Maybe here you can say something about adding new display types, what would be needed for implementing them}
\textcolor{blue}{I am unsure if this can easily be generalized. Some plots are easy to implement (scatterplot), but others like the mosaic plot come with a lot of complications, since that required a deep understanding on how matplotlib works. Implementing new interactive features would be especially challenging.}

@@

The second, $f^c$ is normalized relative to the size of each cluster and can be considered the distribution of features in each cluster. It is useful for comparing the composition of each cluster relative to the features. For example, for $p=4$, if $f^c_{1j} = (0.9, 0.2, 0.1, 0.1)$ it suggests that high values (1's) of feature 1 distinguishes cluster 1, and that values of the other  features were low. In the context of the later examples, this would mean cluster 1 contains tourists that especially engaged in activity 1, but not in activities 2, 3 and 4. This normalisation produces what is called the {\bf intra-cluster fraction}. \textcolor{red}{It corresponds to the cluster means. XXX why not larger values in the example, the maximum would be 1 so 0.4 still seems very moderate.}
\textcolor{blue}{I adjusted the example a bit.}

The last, $f^f$ is normalized relative to each feature, which can be considered to be the distribution of clusters on each feature. It is useful to examine how features are related to a cluster. Considering the last metric, for example, if $f^f_{i1} = (0.2, 0.7, 0, 0.1, 0)$ ($k=5$) would indicate that high values on feature 1 primarily are in cluster 2. In the context of the later examples, this would mean activity 1 is most commonly listed in cluster 2. This normalisation produces what is called the {\bf intra-feature fraction}. \textcolor{red}{Note that this must be interpreted with care in case of inbalanced cluster sizes.}

In this example, while the intra-cluster fraction for cluster 1 and feature 1 is notably high at 0.9, the intra-feature fraction is comparatively low at 0.2. Applied to the subsequent analysis, this indicates that 90 \% of tourists in cluster 1 participated in activity 1, yet only 20 \% of all tourists who engaged in activity 1 were part of cluster 1. The majority of individuals participating in activity 1 were members of cluster 2. This discrepancy may be attributed to cluster 1 representing a relatively small group of tourists, characterized by a pronounced preference for activity 1 and a lack of interest in other activities.
